## Now that football season is upon us, let’s put Linear Algebra to good use!
```{r}
library(pracma)
library(MASS)

df <- read.csv(file = "C:\\Users\\sbyeo\\Downloads\\rating.csv", sep = ',', header = TRUE)
```


### a. Create a Least Square model to relate the dependent variable quarterback rating to the percentage of completions(Pct Comp).
```{r}
rating = matrix(c(df$Rating.Pts), ncol = 1)

pct_comp <- matrix(c(rep(1,length(df$Pct.Comp)), df$Pct.Comp), ncol= 2)

x_hat1 <- ginv(pct_comp)%*%rating
x_hat1
```
>y = B1x + B0

>The equation is rating = 1.746(pct_comp) - 22.033

### b. Create a Least Square model to relate the dependent variable quarterback rating to the percentage of Completions (Pct Comp) and interceptions. (Pct Int)
```{r}
pct_int <- c(df$Pct.Int)

pct_ci = matrix(c(pct_comp, pct_int), ncol = 3)

x_hat2 <- ginv(pct_ci)%*%rating
x_hat2
```
>y = B2x2 + B1x1 + B0

>The equation is rating = -3.076(pct_int) + 1.662(pct_com) - 9.109

### c. Determine the least square error (square root of sum of square errors) for models in part a and b. Does using an extra variable, namely percentage of interceptions, improve the accuracy of the model for this data set? Comment.

***Finding the error for model in part a***
```{r}
Ax_hat1 = pct_comp%*%x_hat1
error_a = norm(rating-Ax_hat1, "2")
error_a
```

***Finding the error for model in part b***
```{r}
Ax_hat2 = pct_ci%*%x_hat2
error_b = norm(rating-Ax_hat2, "2")
error_b
```
>ANSWER FOR C: The addition of an extra variable reduces the error thus improving the accuracy of the model.

### d. Use your models in part a and b to predict the rating for a quarterback with percentage of completions of 60%, and percentage of interceptions of 3%.

***Model a:***
```{r}
rating_a = (matrix(c(1, 60), ncol = 2))%*%x_hat1
rating_a
```
>The predicted rating for model a = 82.704

***Model b:***
```{r}
pct_ci2 = matrix(c(1, 60, 3), ncol = 3)
rating_b = pct_ci2%*%x_hat2
rating_b
```
>The predicted rating for model a = 81.392







